---
title: "Mashhad Population"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Mashhad Population}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
# packpop

## This data provides information about population of Mashhad metropolice based on families,owners, tenants, and so on in each block in 2016. This dataset contains 11 variables and 19943 rows.

### **source:** WWW.amar.org.ir

# Install the package
As a fundamental step, there is a need to install population package if you want to use this data set.

Here is a chunk in order to install the package:

```{r setup, message=FALSE, force = TRUE}
if(!require(remotes)){
    install.packages("remotes")
    library(remotes)
}
remotes::install_github("NiloofarNL/packpop2")
```


Also a summary of this package can be seen by the chunk below:

```{r}
library(packpop2)
summary(pop2016)

```


Following this, there is a list of libraries in this data set:
```{r setup2}
library(packpop2)
library(ggplot2)

```

As mentioned before, this data set has 11 variables 

+---------------+---------------------------------------------------------+
|OBJECTID       |Id of each block as a factor                             |
|               |                                                         |
+---------------+---------------------------------------------------------+
| population    |Number of whole people living in a block                 |
|               |                                                         |
+---------------+---------------------------------------------------------+
| Family        |Number of families living in a block                     |
|               |                                                         |
+---------------+---------------------------------------------------------+
|Owners         |Number of people who has their own property in a block   |
|               |                                                         |
+---------------+---------------------------------------------------------+
|Tenants        |Number of people who rent a property in a block          |
|               |                                                         |
+---------------+---------------------------------------------------------+
|Residential    |Whole number of residential suits in a block             |
|Units          |                                                         |
+---------------+---------------------------------------------------------+
|Apartments     |Number of suits in apartments in a block                 |
|               |                                                         |      
+---------------+---------------------------------------------------------+
|Houses         |Number of village houses in a block                      | 
|               |                                                         |           
+---------------+---------------------------------------------------------+
|Cottage or shed|Number of sheds in a block                               |
|               |                                                         |
+---------------+---------------------------------------------------------+
|Shape_Length   |Surrounding a block in meter scale                       |
|               |                                                         |
+---------------+---------------------------------------------------------+
|Shape_Area     |Surface area of a block in meter scale                   |
|               |                                                         |
+---------------+---------------------------------------------------------+


Also we can see the bar chart of population in each block
```{r}
ggplot(data = pop2016, aes(x = OBJECTID, y = population)) + 
  geom_bar(stat = "identity")
```

